---
title: "SAVANT_Azeri"
output: html_document
date: "2024-05-04"
---
Loading libraries
```{r}
library(lme4)
library(glmm)
library(tidyverse)
library(ggplot2)
library(afex)
library(trimr)
require(car)
require(lattice)
require(itsadug)
library(languageR)
library(plotrix)
library(Hmisc)
library(rlist)
library(effects)
library(sjPlot)
library(effectsize)
library(trimr)
library(palmerpenguins)
library(taylor)
library(emmeans)
library(ggsignif)
```


Loading the raw dataset
```{r}
SAVANT1 = read.csv(file = "140886-v1-7vyf.csv",  header = T)
SAVANT2 = read.csv(file = "140886-v1-p745.csv", header = T)
SAVANT3 = read.csv(file = "140362-v25-p745.csv", header = T)
SAVANT4 = read.csv(file = "140362-v25-7vyf.csv", header = T)
SAVANT5 = read.csv(file = "140886-v2-7vyf.csv", header = T)
SAVANT6 = read.csv(file = "140886-v2-p745.csv", header = T)
```

Combining data
```{r}
SAVANT = rbind(SAVANT1, SAVANT2, SAVANT3, SAVANT4, SAVANT5, SAVANT6)

```


```{r}
colnames(SAVANT)
```

```{r}
cols_to_keep <- c("Participant.Private.ID",
  "Reaction.Time",
  "Participant.Status",
  "Participant.Completion.Code",
  "Participant.Device.Type",
  "Trial.Number",
  "Response.Type",
  "Response",
  "Correct",
  "Display",
  "Component.Name",
  "Spreadsheet..condition",
  "Spreadsheet..answer",
  "Spreadsheet..item",
  "Spreadsheet..trial",
  "Spreadsheet..Freq",
  "Spreadsheet..set",
  "Object.ID",
  "Response.Type"
)
```

```{r}
SAVANT_Data <- select(SAVANT, all_of(cols_to_keep)
)
```

```{r}
n_distinct(SAVANT_Data$Participant.Private.ID)
```
```{r}
unique(SAVANT_Data$Participant.Private.ID)
```
```{r}
view(SAVANT_Data)
```

Loading Questionnaires
```{r}
questionnaire1 <- read.csv("140886-v1-questionnaire-e274.csv")
questionnaire2 <- read.csv("140362-v25-questionnaire-e274.csv")
questionnaire3 <- read.csv("140886-v2-questionnaire-e274.csv")
```

Combining questionnaires
```{r}
questionnaire <- rbind(questionnaire1,questionnaire2,questionnaire3)
```

```{r}
unique(questionnaire$Participant.Private.ID)
```


```{r}
colnames(questionnaire)
```


```{r}
cols_to_keep <- c("Participant.Private.ID",
                  "Participant.Status",
                  "Participant.Device.Type",
                  "Question",
                  "Response",
                  "Object.ID",
                  "Key"
)

Questionnaire <- select(questionnaire, all_of(cols_to_keep))
```

```{r}
n_distinct(Questionnaire$Participant.Private.ID)
```
```{r}
view(Questionnaire)
```

Looking at timedouts
We don't need to remove timedouts because they have already been labelled as "screen" in the object.ID column instead of object number. 
```{r}
SAVANT_Timedouts <- SAVANT_Data %>% filter(Response.Type == "timedOut")
```

Checking whether participants have used mobile phones and if so I need to exclude them from data.
Device type in task data:
```{r}
table(SAVANT_Data$Participant.Private.ID,SAVANT_Data$Participant.Device.Type)
```
Device type in questionnaire:
```{r}
table(Questionnaire$Participant.Private.ID,Questionnaire$Participant.Device.Type)
```


```{r}
colnames(SAVANT_Data)
```
```{r}
colnames(Questionnaire)
```


Renaming columns
```{r}
SAVANT_Data <- SAVANT_Data %>% 
  rename(
  Participant = Participant.Private.ID,
  Completion.Code= Participant.Completion.Code,
  Device.Type = Participant.Device.Type,
  RT = Reaction.Time,
  Accuracy = Correct,
  Condition = Spreadsheet..condition,
  Answer = Spreadsheet..answer,
  Item = Spreadsheet..item,
  Trial = Spreadsheet..trial,
  Freq = Spreadsheet..Freq,
  Set = Spreadsheet..set,
  Object = Object.ID
  )
```


```{r}
Questionnaire <- Questionnaire %>% 
  rename(
  Participant = Participant.Private.ID,
  Device.Type = Participant.Device.Type,
  Object = Object.ID
)
```


looking at age range 
```{r}
Age <- Questionnaire %>% 
  filter(Object == "object-13") %>% 
  distinct(Participant, Response)

```

```{r}
Questionnaire <- Questionnaire %>% 
  mutate( Response = str_replace_all(Response, "۴۲","42"))

Questionnaire <- Questionnaire %>% 
  mutate( Response = str_replace_all(Response, "36 سال", 
                                       "36"))
```

```{r}
Age <- Questionnaire %>% 
  filter(Object == "object-13") %>% 
  distinct(Participant, Response)
```
Participant 9287678 is under the age of 18 and needs to be excluded.

Mean age of participants 
changing age to a numeric value and calculating mean 
```{r}
age_numeric <- as.numeric(Age$Response)
str(age_numeric)
mean(age_numeric)
range(age_numeric)
```

Where were participants born?
```{r}
Place_of_Birth <- Questionnaire %>% 
  filter(Object == "object-15") %>% 
  distinct(Participant, Response)

```

Questions in questionnaire include self-assessed language proficiency and language use. 
Object-40: Language use- Speaking in Azeri 
Object-76: Language use- Listening in Azeri 
Object-77: Language use- Writing in Azeri 
Object-82: Language use- Reading in Azeri 
Object-86: Self-proficiency in speaking in Azeri
Object-88: Self-proficiency in listening in Azeri 
Object-89: Self-proficiency in reading in Azeri
Object-92: Self-proficiency in writing in Azeri
Object-41: Language use- Speaking in Persian
Object-78: Language use- Listening in Persian
Object-80: Language use- Writing in Persian
Object-83: Language use- Reading in Persian


```{r}
str(Questionnaire)
```
Converting characters to numeric in the response column 
```{r}
Questionnaire <- Questionnaire %>% mutate(
  Response = as.numeric(Response)
)
str(Questionnaire)

```
To calculate the mean for self-assessed  proficiency in speaking I need to filter for object-86:
```{r}
Prof_Speak <- Questionnaire %>% filter(Object == "object-86")
```
2 participants have rated their proficiency in speaking as bad as 1. 

Mean of self-assessed proficiency in speaking 
```{r}
Mean_Prof_Speak <- Prof_Speak %>% 
  summarise(Mean_Speaking = mean(as.numeric(Response))/7*100
)

```

Mean of self-assessed proficiency in listening in Azeri 
```{r}
Prof_Listen <- Questionnaire %>% 
  filter(Object == "object-88")

Mean_Prof_Listen <- Prof_Listen %>% 
  summarise(Mean_Listening = mean(as.numeric(Response))/7*100
)

```

Mean of self-assessed proficiency in reading in Azeri
```{r}
Prof_Read <- Questionnaire %>% 
  filter(Object == "object-89")

Mean_Prof_Read <- Prof_Read %>% 
  summarise(Mean_Reading=mean(as.numeric(Response))/7*100
)

```

Mean of self-assessed proficiency in writing in Azeri
```{r}
Prof_Write <- Questionnaire %>% 
  filter(Object == "object-92")

Mean_Prof_Write <- Prof_Write %>% 
  summarise(Mean_Writing=mean(as.numeric(Response))/7*100
)

```

Mean of self-assessed proficiency in four skills in Azeri per participant 
```{r}
Self_Assess_Prof <- Questionnaire %>% 
  filter(Object =="object-86"|Object == "object-88"|Object == "object-89"|Object == "object-92"
)

Mean_Prof <- Self_Assess_Prof %>% 
  group_by(Participant) %>% 
  summarise(Mean_Proficiency=mean(as.numeric(Response))/7*100) %>% 
  arrange(Mean_Proficiency)

str(Mean_Prof)
```
Merging mean of proficiency to the data
```{r}
SAVANT_Data <- merge(Mean_Prof,SAVANT_Data, by=c("Participant")
)

```

```{r}
n_distinct(SAVANT_Data$Participant)
```
```{r}
unique(SAVANT_Data$Participant)
```

Language use in Azeri:
Data was filtered for language use in four skills of speaking, listening, reading and writing in Azeri

```{r}
Lan_Use <- Questionnaire %>% 
  filter(Object =="object-40"|Object == "object-76"|Object == "object-77"|Object == "object-82"
)

```
Mean of language use in four skills by participant
```{r}
Mean_LanUse <- Lan_Use %>% 
  group_by(Participant) %>% 
  summarise(Mean_LanUse=mean(as.numeric(Response))
  ) %>%
  arrange(Mean_LanUse)

```
Merging language use mean rates to the data
```{r}
SAVANT_Data <- merge(Mean_LanUse, SAVANT_Data, by=c("Participant")
)

```

Mean of language use in speaking in Azeri
```{r}
LanUse_Speak <- Questionnaire %>% 
  filter(Object =="object-40")

Mean_Use_Speak <- LanUse_Speak %>% 
  summarise(Mean_Speaking=mean(as.numeric(Response))
)

```
Mean of language use in listening in Azeri
```{r}
LanUse_Listen <- Questionnaire %>% 
  filter(Object == "object-76")

Mean_Use_Listen <- LanUse_Listen %>% 
  summarise(Mean_Listening=mean(as.numeric(Response))
)

```

Mean of language use in writing in Azeri
```{r}
LanUse_Write <- Questionnaire %>% 
  filter(Object == "object-77")

Mean_Use_Write <- LanUse_Write %>% 
  summarise(Mean_Writing=mean(as.numeric(Response))
)
```

Mean of language use in reading in Azeri
```{r}
LanUse_Read <- Questionnaire %>% 
  filter(Object == "object-82")

Mean_Use_Read <- LanUse_Read %>% 
  summarise(Mean_Reading=mean(as.numeric(Response))
)
```

Mean of language use in speaking in Persian
```{r}
LanUse_Fa_Speak <- Questionnaire %>% 
  filter(Object == "object-41")

Mean_Use_Fa_Speak <- LanUse_Fa_Speak %>% 
  summarise(Mean_Fa_Speak=mean(as.numeric(Response))
)
```

Mean of language use in listening in Persian
```{r}
LanUse_Fa_Listen <- Questionnaire %>% filter(Object == "object-78")

Mean_Use_Fa_Listen <- LanUse_Fa_Listen %>% summarise(Mean_Fa_Listen=mean(as.numeric(Response))
)
```

Mean of language use in writing in Persian
```{r}
LanUse_Fa_Write <- Questionnaire %>% 
  filter(Object == "object-80")

Mean_Use_Fa_Write <- LanUse_Fa_Write %>% 
  summarise(Mean_Fa_Write=mean(as.numeric(Response))
)
```

Mean of language use in reading in Persian
```{r}
LanUse_Fa_Read <- Questionnaire %>% 
  filter(Object == "object-83")

Mean_Use_Fa_Read <- LanUse_Fa_Read %>% 
  summarise(Mean_Fa_Read=mean(as.numeric(Response))
)
```

Mean of language use in four skills in Persian
```{r}
Lan_Use_Persian <- Questionnaire %>% 
  filter(Object =="object-41"|Object == "object-78"|Object == "object-80"|Object == "object-83"
)
```

```{r}
Mean_LanUse_Persian <- Lan_Use_Persian %>% 
  group_by(Participant) %>% 
  summarise(Mean_LanUse_Persian=mean(as.numeric(Response))
  ) %>%
  arrange(Mean_LanUse_Persian)
```

Merging language use mean rates in Persian to the data
```{r}
SAVANT_Data <- merge(Mean_LanUse_Persian, SAVANT_Data, by=c("Participant")
)
```

Checking for keyboard response: This includes keyboard response in both practice and critical trials. The reason that I filtered for "keyboard response" is that it is incorporated in two screens in the experiment: both audio screen and response screen.  
Practice trials include objects 122 and 112.
Critical trials include objects 121 and 124.
```{r}
colnames(SAVANT_Data)
```

```{r}
SAVANT_KEY <- SAVANT_Data %>% 
  filter(Component.Name == "Keyboard Response")
unique(SAVANT_KEY$Object)
```
Checking for object 124 (Object 124 is the keyboard response in the audio screen)
Some participants have responded to items before audio finishes or exactly when audio finishes, i.e. in object-124 
```{r}
SAVANT_124 <- SAVANT_Data %>% 
  filter(Set == "critical",Object == "object-124")
nrow(SAVANT_124)
```

What's the number of trials in object 121 of the critical set?
```{r}
SAVANT_121 <- SAVANT_Data %>% 
  filter(Set == "critical",Object == "object-121") 

nrow(SAVANT_121)
```
Most trials have been responded in object 121.

Looking at the number of accurate responses in object 121
```{r}
table(SAVANT_121$Accuracy)
```
Looking at the number of accurate responses in object 124 
```{r}
table(SAVANT_124$Accuracy)
```
A mistake: Grammatical harmony items have been labeled as unacceptable in the spreadsheet in Gorilla 
```{r}
Everything_other_data <- SAVANT_Data %>% filter(Condition != "GramHarm") #filtering for all data except grammatical harmony items
GramHarm_crit_data <- SAVANT_Data %>% filter(Condition == "GramHarm") %>% filter(Set == "critical") #filtering for grammatical harmony items in the critical set

GramHarm_crit_data["Accuracy"][GramHarm_crit_data["Accuracy"] == 0] <- 2
GramHarm_crit_data["Accuracy"][GramHarm_crit_data["Accuracy"] == 1] <- 0
GramHarm_crit_data["Accuracy"][GramHarm_crit_data["Accuracy"] == 2] <- 1

GramHarm_noncrit_data <- SAVANT_Data %>% filter(Condition == "GramHarm") %>% filter(Set != "critical")

SAVANT_Task <- rbind(GramHarm_crit_data,Everything_other_data,GramHarm_noncrit_data)
```

```{r}
view(SAVANT_Task)
colnames(SAVANT_Task)
```
Filtering for object 121 and 124
```{r}
Task_Critical_121_124 <- SAVANT_Task %>% 
  filter(Set == "critical") %>%
  filter(Object == "object-121" | Object == "object-124")

```

Creating a column with a unique trial number to be able to choose 
```{r}
Task_Critical_121_124$TrialUniqueID <- paste(Task_Critical_121_124$Participant," / ", Task_Critical_121_124$Trial.Number)

```

Filtering for data where participants responded in both object 124 and 121 and then filtering for only object 124
```{r}
TrialWithBoth = Task_Critical_121_124$TrialUniqueID[Task_Critical_121_124$Object == "object-121" & Task_Critical_121_124$TrialUniqueID %in% Task_Critical_121_124$TrialUniqueID[Task_Critical_121_124$Object == "object-124"]]

SAVANT_critical = Task_Critical_121_124[!(Task_Critical_121_124$TrialUniqueID %in% TrialWithBoth & Task_Critical_121_124$Object == "object-121"),]
```

Filler trials
```{r}
SAVANT_filler <- SAVANT_Task %>% 
  filter(Set == "filler") %>%
  filter(Object == "object-121" | Object == "object-124")
```

```{r}
SAVANT_filler$TrialUniqueID2 <- paste(SAVANT_filler$Participant," / ", SAVANT_filler$Trial.Number)

TrialWithBoth = SAVANT_filler$TrialUniqueID2[SAVANT_filler$Object == "object-121" & SAVANT_filler$TrialUniqueID2 %in% 
SAVANT_filler$TrialUniqueID2[SAVANT_filler$Object == "object-124"]]

SAVANT_filler = SAVANT_filler[!(SAVANT_filler$TrialUniqueID2 %in% TrialWithBoth & SAVANT_filler$Object == "object-121"),]
```

Now I have 2 separate data for critical and filler trials: SAVANT_critical, SAVANT_filler

Participants in the filler trials
```{r}
unique(SAVANT_filler$Participant)
```
Which participants didn't respond to fillers or critical trials?
```{r}
Participant_data <- SAVANT_Task$Participant
Participant_filler <- SAVANT_filler$Participant
Participant_critical <- SAVANT_critical$Participant
```

```{r}
Bad_Participants_Critical <- setdiff(Participant_data, Participant_critical)
Bad_Participants_Critical
```
```{r}
Bad_Participants_Filler <- setdiff(Participant_data, Participant_filler)
Bad_Participants_Filler
```
Let's find out why these participants didn't respond to the trials
```{r}
Bad_Participants_Data_Critical <- SAVANT_Task %>% 
  filter(Participant %in% Bad_Participants_Critical) %>%
  filter(Object == "object-124" | Object == "object-121")
```
They have not responded to the trials. Their keyboards might not be working or they have missed to respond.

```{r}
Bad_Participants_Data <- SAVANT_Task %>% filter(Participant %in% Bad_Participants_Critical)

```

```{r}
Questionnaire_Bad_Participants <- Questionnaire %>% filter(Participant %in% Bad_Participants_Critical)

```
Two participants have not responded to the trials: One of the participants is from Zanjan and 34 years old and the other is from Maragheh and 22 years old.
The third participant is the one who answered with a mobile phone: 9458745

These participants will be removed from the data

Removing Bad Participants
```{r}
SAVANT_Task <- SAVANT_Task[!SAVANT_Task$Participant %in% Bad_Participants_Critical,]
SAVANT_filler <- SAVANT_filler[!SAVANT_filler$Participant %in% Bad_Participants_Critical,]
SAVANT_critical <- SAVANT_critical[!SAVANT_critical$Participant %in% Bad_Participants_Critical,]
```

Changing character/integer variables into factors in filler trials
```{r}
SAVANT_filler <- SAVANT_filler %>% 
  mutate (Participant = as.factor(Participant),
          Trial.Number = as.factor(Trial.Number),
          Condition = as.factor(Condition),
          Item = as.factor(Item),
          Trial = as.factor(Trial),
          Freq = as.factor(Freq)
    )
summary(SAVANT_filler)
```
Changing character/integer variables into factors in critical trials
```{r}
SAVANT_critical <- SAVANT_critical %>% 
  mutate (Participant.Private.ID = as.factor(Participant),
          Trial.Number = as.factor(Trial.Number),
          Condition = as.factor(Condition),
          Item = as.factor(Item),
          Trial = as.factor(Trial),
          Freq = as.factor(Freq)
    
          
  )
summary(SAVANT_critical)
```
```{r}
table_correct_critical <- SAVANT_critical %>% 
  count(Participant, Accuracy) %>% 
  spread(Accuracy, n) %>% 
  mutate(prop.accuracy = `1`/168) %>% 
  mutate(prop.accuracy = round(prop.accuracy, 2)) %>% 
  arrange(prop.accuracy)

table_correct_critical
view(table_correct_critical)
```

```{r}

table_correct_filler <- SAVANT_filler %>% 
  count(Participant, Accuracy) %>% 
  spread(Accuracy, n) %>% 
  mutate(across(c("0", "1"), ~ ifelse(is.na(.), 0,.))) %>%
  mutate(prop.Accuracy = `1`/24) %>% 
  mutate(prop.Accuracy = round(prop.Accuracy, 2)) %>% 
  arrange(prop.Accuracy)

table_correct_filler
view(table_correct_filler)
```
I'll remove participants that have accuracy rate of less than 70% in the filler trials.
The forth participant is 16 years old and needs to be removed from the data.
```{r}

Participant_high_error <- list(9345406, 9237013, 9401799, 9287678)
SAVANT_Task <- SAVANT_Task[!SAVANT_Task$Participant %in% Participant_high_error,]
SAVANT_filler <- SAVANT_filler[!SAVANT_filler$Participant %in% Participant_high_error,]
SAVANT_critical <- SAVANT_critical[!SAVANT_critical$Participant %in% Participant_high_error,]

```

```{r}
colnames(SAVANT_critical)
```
Accuracy mean, SD and SE 
```{r}
Acc_mean <- SAVANT_critical %>% group_by(Condition) %>% summarise(Mean = round(mean(Accuracy),2), SD = round(sd(Accuracy),3), SE = round(std.error(Accuracy),4))
view(Acc_mean)                                                                 
```

Accuracy plot by average:
```{r}
SAVANT_critical %>% group_by(Condition, Item) %>%
  summarise(prop = mean(Accuracy)) %>%
  ggplot(aes(x= Condition , y= prop)) +
  stat_summary(fun.data = mean_cl_boot, size=0.75) + 
  geom_jitter(size = 0.5, alpha = 0.5, width = 0.2, height = 0) +
  xlab("Condition") +
  ylab("Accuracy")
```

```{r}

ggplot(Acc_mean,
       aes(x=Condition,y=Mean*100,fill = Condition)) +
  
 
  geom_bar(stat = "identity", width = 0.7, position = position_dodge(0.7), show.legend = FALSE  )+
  ylab("% Accuracy") + 
  xlab("Conditions") +
  coord_cartesian(ylim = c(0, 100)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))+
  geom_signif(
    comparisons = "Condition",
    margin_top = 0.12,
    step_increase = 0.09,
    tip_length = 0.05,
    annotation = c("***")
  )
```

Accuracy rates: Generalised Linear Modeling

Response: Accuracy
Predictors: 1. Condition, 2. Trial, 3. Participant, 4. Frequency 

```{r}
SAVANT_critical$Condition <- relevel(SAVANT_critical$Condition, ref = "Gramm.Simple") 
```


```{r}
acc.m1 <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = SAVANT_critical, family = "binomial", control = glmerControl(optimizer = "bobyqa"))
summary(acc.m1)
```
```{r}
tab_model(acc.m1)
```

```{r}
emmeans(acc.m1, pairwise ~ Condition, adjust = "bonferroni")
```


Harmony manipulation: Grammatical Harmony vs Harmony Violation
```{r}
Harmony_Accu <- SAVANT_critical %>% filter(Condition == "GramHarm" | Condition == "HarmViol" )
```

```{r}
Acc_HarmViol_Model <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = Harmony_Accu, family = "binomial", control = glmerControl(optimizer = "bobyqa"))
summary(Acc_HarmViol_Model)
tab_model(Acc_HarmViol_Model)
```
```{r}
emmeans(Acc_HarmViol_Model, pairwise ~ Condition, adjust = "bonferroni")
```
-lar category manipulation (gramsimple vs. synviolpl)
```{r}
Syn_Pl_Accu <- SAVANT_critical %>% filter(Condition == "SynViol.Pl" | Condition == "Gramm.Simple" )
```

```{r}
Acc_SynViolPl_Model <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = Syn_Pl_Accu, family = "binomial", control = glmerControl(optimizer = "bobyqa"))
summary(Acc_SynViolPl_Model)
```
```{r}
emmeans(Acc_SynViolPl_Model, pairwise ~ Condition, adjust = "bonferroni")
```
Num X-lar manipulation (GramNum, SynViolNum, SemViol)

```{r}
NumViol_Accu <- SAVANT_critical %>% filter(Condition == "Gramm.Num" | Condition == "SynViol.Num" | Condition == "SemViol" )
```

```{r}
Acc_SynViolNum_Model <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = NumViol_Accu, family = "binomial", control = glmerControl(optimizer = "bobyqa"))
summary(Acc_SynViolNum_Model)
```
```{r}
emmeans(Acc_SynViolNum_Model, pairwise ~ Condition, adjust = "bonferroni")
```
Comparing semantic violation vs syntactic violation plural
```{r}
Sem_Syn_Pl_Viol_Accu <- SAVANT_critical %>% filter(Condition == "Gramm.Num" | Condition == "SynViol.Pl" | Condition == "SemViol" )
```

```{r}
Acc_Sem_Syn_Pl_Viol_Model <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = NumViol_Accu, family = "binomial", control = glmerControl(optimizer = "bobyqa"))
summary(Acc_Sem_Syn_Pl_Viol_Model)
```
```{r}
emmeans(Acc_Sem_Syn_Pl_Viol_Model, pairwise ~ Condition, adjust = "bonferroni")
```



Reaction Time 

```{r}
SAVANT_Task$TrialUniqueID <- paste(SAVANT_Task$Participant," / ", SAVANT_Task$Trial.Number)

```


```{r}
TrialWithBoth = SAVANT_Task$TrialUniqueID[SAVANT_Task$Object == "object-121" & SAVANT_Task$TrialUniqueID %in% 
SAVANT_Task$TrialUniqueID[SAVANT_Task$Object == "object-124"]]

SAVANT_Task = SAVANT_Task[!(SAVANT_Task$TrialUniqueID %in% TrialWithBoth & SAVANT_Task$Object == "object-121"),]
```


```{r}
Data_121 <- SAVANT_Task %>% filter(Object == "object-121")
Data_44_continue <- SAVANT_Task %>% filter(Object == "object-44" & Response.Type == "continue")
Data_121_44 <- rbind(Data_121, Data_44_continue)
```

```{r}
RT_121 <- Data_121_44 %>% group_by(TrialUniqueID) %>%
  summarise(Total_RT = sum(RT))

```

```{r}
Data_121_final <- merge(RT_121, Data_121, by = c("TrialUniqueID"))
```

```{r}
Data_124 <- SAVANT_Task %>% filter(Object == "object-124")
Data_44_audio_started <- SAVANT_Task %>% filter(Object == "object-44" & Response == "audio started")
Data_124_44 <- rbind(Data_124, Data_44_audio_started)

```

```{r}
RT_124 <- Data_124_44 %>% group_by(TrialUniqueID) %>%
  arrange(TrialUniqueID, Object) %>%
  mutate(Total_RT = lag(RT) - RT) %>%
  filter(!is.na(Total_RT)) %>%
  select(Total_RT, TrialUniqueID)
  

```

```{r}
Data_124_final <- merge(Data_124, RT_124, by = c("TrialUniqueID"))
```

Combining both 121 and 124
```{r}
Data_121_124 <- rbind(Data_124_final, Data_121_final)
```

Filtering for correct answers in order to generate means for reaction time 
```{r}
SAVANT_RT <- Data_121_124 %>% filter(Accuracy == 1, Set == "critical")

view(SAVANT_RT)
```

```{r}
str(SAVANT_RT)
```
```{r}
summary(SAVANT_RT$Total_RT)
```

```{r}
qqnorm(SAVANT_RT$Total_RT)
```


```{r}

SAVANT_RT2 <- SAVANT_RT %>% filter(Total_RT > 200)
(nrow(SAVANT_RT) - nrow(SAVANT_RT2)) / nrow(SAVANT_RT)*100

```
Checking whether data is normaly distributed

```{r}
SAVANT_RT2$Log_RT <- log(SAVANT_RT2$Total_RT)
```

```{r}
qqnorm(SAVANT_RT2$Log_RT)
```


```{r}
hist(SAVANT_RT2$Total_RT, xlab = "Reaction Time")
```

Checking how the distribution look like for the random factor of participant 
```{r}

qqmath(~Log_RT|Participant, data = SAVANT_RT2)

```
```{r}
table(SAVANT_RT2$Participant)
```
box whisker plots per condition 
```{r}
bwplot(Total_RT ~ Condition, data = SAVANT_RT2 )
```
The reason that syntactic plural violation items have been responded to faster compared with syntactic numeral violatiuon is probably because SynViol.Num items are longer in syllable. 

One thing about syntactic violation plurals is that the violation is the lack of tense, 
i.e oxu-lar (read-plural) is ungrammatical while oxu-du-lar (read-past-plural) is grammatical.


Reaction Time means per condition and standard error and standard deviation 
```{r}
SAVANT_RT_means <- SAVANT_RT2 %>% group_by(Condition) %>% summarise(Mean = round(mean(Total_RT),2), Standard_Deviation = round(sd(Total_RT),2), Standard_Error = round(std.error(Total_RT),3)
)

view(SAVANT_RT_means)
```

Let's look at the effect of fatigue
```{r}
xylowess.fnc(Total_RT ~ Trial | Participant, data = SAVANT_RT2, ylab = "log RT")
```
```{r}
str(SAVANT_RT2)
```
```{r}
SAVANT_RT2 <- SAVANT_RT2 %>% mutate (Participant = as.factor(Participant),
          Trial.Number = as.factor(Trial.Number),
          Condition = as.factor(Condition),
          Item = as.factor(Item),
          Trial = as.factor(Trial),
          Freq = as.factor(Freq)
    )
```


```{r}
SAVANT_RT2$Condition <- relevel(SAVANT_RT2$Condition, ref = "Gramm.Simple") 
```


```{r}
RT_M1 <- lmer(Total_RT ~ Condition + (1  | Participant) + (1  | Trial), data=SAVANT_RT2)
tab_model(RT_M1)
summary(RT_M1)
```

Let's extract fitted values and compare these with the actual values
```{r}
fitted(RT_M1)[1:4]
```
```{r}
SAVANT_RT2$Total_RT[1:4]
```


Harmony manipulation (gramharm vs. harmviol)
```{r}
RT_Harmony <- SAVANT_RT2 %>%
  filter(Condition == "HarmViol" | Condition == "GramHarm")
```


```{r}
RT_Harmony_Model <- lmer(Total_RT ~ Condition + (1  | Participant) + (1  | Trial), data = RT_Harmony)
tab_model(RT_Harmony_Model)
summary(RT_Harmony_Model)
```

```{r}
emmeans(RT_Harmony_Model, pairwise ~ Condition, adjust = "bonferroni")
```

-lar category manipulation (gramsimple vs. synviolpl)
```{r}
RT_SynViolPl <- SAVANT_RT2 %>%
  filter(Condition == "Gramm.Simple" | Condition == "SynViol.Pl")
```


```{r}
RT_SynViolPl_Model <- lmer(Total_RT ~ Condition + (1  | Participant) + (1  | Trial), data = RT_SynViolPl)
tab_model(RT_SynViolPl_Model)
summary(RT_SynViolPl_Model)
```
```{r}
emmeans(RT_SynViolPl_Model, pairwise ~ Condition, adjust = "bonferroni")
```

Num X-lar manipulation (GramNum, SynViolNum, SemViol)
```{r}
RT_SynViolNum <- SAVANT_RT2 %>%
  filter(Condition == "Gramm.Num" | Condition == "SynViol.Num" | Condition == "SemViol" )

```

```{r}
RT_SynViolNum_Model <- lmer(Total_RT ~ Condition + (1  | Participant) + (1  | Trial), data = RT_SynViolNum)
tab_model(RT_SynViolNum_Model)
summary(RT_SynViolNum_Model)
```

```{r}
emmeans(RT_SynViolNum_Model, pairwise ~ Condition, adjust = "bonferroni", pbkrtest.limit = 3113)
```

```{r}
Sem_Syn_Pl_Viol_RT <- SAVANT_RT2 %>% 
  filter(Condition == "Gramm.Num" | Condition == "SynViol.Pl" | Condition == "SemViol" )
```

```{r}
Sem_Syn_Pl_Viol_RT_Model <- glmer (Accuracy ~ Condition + (1  | Participant) + (1  | Trial), data = Sem_Syn_Pl_Viol_RT, family = "binomial", control = glmerControl(optimizer = "bobyqa"))

summary(Sem_Syn_Pl_Viol_RT_Model)
```
```{r}
emmeans(Sem_Syn_Pl_Viol_RT_Model, pairwise ~ Condition, adjust = "bonferroni")
```



















